a Change again
# Code-a-thon Project Template

This project is intended to help you apply your skills in R in a way that would be conducive for collaborating or creating reproducible analyses.


## Data Used

Identify a dataset to analyze. Remember that if you share the data you must **not violate any privacy restrictions**

If you don't have your own data, options for places to find data are listed on https://daseh.org.

You might start by setting up an R Project, importing your data, previewing the data, etc. 

This dataset tracks the updates made on the dataset "COVID-19 Community Vulnerability Crosswalk - Rank Ordered by Score"


```{r}


COVID_19_Community_Vulnerability_Crosswalk_Rank_Ordered_by_Score_ <- read_csv("C:/Users/lucym/Downloads/COVID-19_Community_Vulnerability_Crosswalk_-_Rank_Ordered_by_Score_.csv")

covid_19_ranked_by_score <- COVID_19_Community_Vulnerability_Crosswalk_Rank_Ordered_by_Score_
covid_19_ranked_by_score

#rename columns hardest hit area,   `Low Income Area (LIA) Census Tract (Poverty Percentage)`, 



```

**describe** what your data looks like and **where** you got it. Identify what the variables and samples are, or point to a data dictionary. Describe how the data was originally created. 

Data from healthcare.gov- COVID-19 community vulnerability crosswalk (ordered by score)

Looks at communities down to the census track based of four key datasets
Hardest hit area (HHA) (sustained hotspot + hotspot )
Low income area (LIA)
Tribal community 
Rural community 






# Data Cleaning/Wrangling

Perform any data subsetting, cleaning, or manipulation methods that were described in this course on your data. Examples are: renaming the columns, recoding values, reshaping the data, filtering the data etc. 

You might also research other methods to include here, especially if your data is very unique.

```{r}

#looked at the different variables 

rename_covid_19 <- rename(covid_19_ranked_by_score, 
"State" = STATE,
"Low_Income_Census_Tract" = 'Low Income Area (LIA) Census Tract (Poverty Percentage)',
"Hardest_hit_area" = 'Hardest Hit Area (HHA)',
)


covid_19_ranked_by_score <- rename_covid_19

#select(covid_19_ranked_by_score, State, County)
     
    # County, Max Possible Score, Hardest_hit_area, HHA,  Low_Income_Census_Tract)




```

```{r}
#select(covid_19_ranked_by_score, State, Hardest_hit_area, Low_Income_Census_Tract)



covid_19_ranked_by_score_WA <-covid_19_ranked_by_score%>% 
mutate(Low_Income_Census_Tract_Percentage = Low_Income_Census_Tract * 100)%>% 
   filter(State == "WASHINGTON", Hardest_hit_area %in% c("SustainedHotspot","Hotspot"))%>% 
    select(State, County, Hardest_hit_area, Low_Income_Census_Tract_Percentage )%>% 
      drop_na(County,Low_Income_Census_Tract_Percentage) %>% 
        group_by(Hardest_hit_area) 
  



covid_19_ranked_by_score_WA




```
##July 30th Tuesday 
#filter by sustained hotspots 
#filter by location WA state 
# drop na values 
# multiply low income tract by 100 
#group_by(Hardest_hit_area)

#ctrl+shift+m %>% 
#

%>% 
#summarize(average_low_income_census_tract = mean(Low_Income_Census_Tract_Percentage))

covid_19_ranked_by_score_WA <- covid_19_ranked_by_score %>% 
  mutate(Low_Income_Census_Tract_Percentage = Low_Income_Census_Tract * 100) %>% 
  filter(State == "WASHINGTON" & Hardest_hit_area == "SustainedHotspot") %>% 
  select(State, County, Low_Income_Census_Tract, Hardest_hit_area) %>% 
  drop_na(County) 
covid_19_ranked_by_score_WA







# Data Visualization

Create some visualizations of your data using the esquisse app or the ggplot2 package.

```{r}



ggplot(covid_19_ranked_by_score_WA) +
  aes(
    x = County,
    y = Low_Income_Census_Tract_Percentage,
    fill = Hardest_hit_area
  ) +
  geom_col() +
  scale_fill_hue(direction = 1) +
  theme_minimal() +
  ylim(0, 100)



```


# Data Analysis

Perform a **simple analysis** of your data. This can involve summarizing the data to describe aspects about it (quartiles, means, range etc.) or a simple statistical test. 

Don't forget to describe what analysis you performed and why. Provide some simple **interpretation** about what your analysis might indicate about your data.

```{r}




```


# Please include additional sections as desired.

```{r}

```


# Versions

Include some information about the version of R and the packages you are using by running sessionInfo().

```{r}
sessionInfo()
```

Render your document to an html or pdf using the "Knit" button.
